Differentially Private Bayesian Inference

### 2018-04-10 main.tex
update

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(z) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
&  \leq e^{\frac{\epsilon}{2}} \cdot \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
exp(\frac{\epsilon \hat{s}}{2 S(x)})
& \leq e^{\frac{\epsilon}{2}} \cdot exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
\frac{\epsilon \hat{s}}{2 S(x)}
& \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
\hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
(1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
\end{split}
\end{equation*}

To proof this, we consider some cases:

@@

>>>>

\begin{equation*}
\underset{r \thicksim \expomech}{Pr}[u(r) = z]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \expomech}{Pr}[u(r) = e^{\lambda} z] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

@@

% \begin{equation*}
% \begin{split}
% \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
% &  \leq e^{\frac{\epsilon}{2}} \cdot \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
% exp(\frac{\epsilon \hat{s}}{2 S(x)})
% & \leq e^{\frac{\epsilon}{2}} \cdot exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
% \frac{\epsilon \hat{s}}{2 S(x)}
% & \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
% \hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
% (1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
% \end{split}
% \end{equation*}

@@

We set the $h(z) = Pr[u(\expomech) = z] = \frac{exp(\frac{\epsilon z}{2 S(x)})}{NL_x}$.

We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(z)}{h(e^{\lambda}z)} = \frac{exp(\frac{\epsilon z}{2 S(x)})}{exp(\frac{\epsilon (z \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(z)}{h(e^{\lambda}z)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\expomech) (1 - e^{\lambda})}{S(x)})$. Consider the event $G = \{ \expomech : u(\expomech) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(z)$ is $1 - \frac{\delta}{2}$. Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$. The $\beta$ is set as
